Persistence in functional topology and a correction to a theorem of Morse

### 2021-07-16 connectivity.tex
Improve sect 4

Concretely, let $\H = (\H_d)_{d \in \Z} \colon \Top \to \Vect$ be a fixed graded homotopy invariant functor, which we call \emph{homology}.
A triple of spaces $X_{1}, X_{2} \subseteq X$ is said to have a \emph{Mayer-Vietoris sequence} for $\H$ if the inclusion-induced maps fit in a long exact sequence
 \[
\begin{tikzcd}[column sep = small]
\cdots \arrow[r] & \H_{n}(X_{1} \cap X_{2}) \arrow[r] & \H_{n}(X_{1}) \oplus \H_{n}(X_{2}) \arrow[r] & \H_{n}(X) \arrow[r] & \H_{n-1}(X_{1} \cap X_{2}) \arrow[r] & \cdots \ .
\end{tikzcd}
\]
We say that $\H$ has the \emph{open} (resp.\@\  \emph{compact}) \emph{Mayer-Vietories property} if there are natural Mayer-Vietoris sequences for all triples $X_{1}, X_{2} \subseteq X$ with $X = X_1 \cup X_2$ and $X_i \subseteq X$ open (resp.\@\ compact Hausdorff).

For the rest of this section, we will assume that $\H$ has either the open or the compact Mayer-Vietoris property and that there is some $n_0$ such that $\H_{n}$ is 0 for all $n \leq n_0$. 
Note that this includes singular homology with field coefficients, which, like any homology theory in the sense of the Eilenberg-Steenrod axioms \cite[Section I]{MR0050886}, has the open Mayer-Vietoris property, and it also includes \v{C}ech homology with field coefficients, which has the closed Mayer-Vietoris property.
%We prioritize the reduced versions of these theories, which motivates our notation for a generic homology $\H$.

\begin{defi} \label{defi:local_connectedness}
	For $n \in \Z$ a continuous map is said to be \textit{$n$-homologically small} ($\HS_n$) if the image of the map induced by $\H_{n}$ is finite dimensional.
	%Furthermore, if that image is $0$ then we say that the map is \textit{$n$-homologically trivial} ($\HT_n$).
	%The map is said to be \textit{$n$-homotopically trivial} $(\piT_{n})$ if the map induced by $\pi_{n}$ is 0.
	We omit references to $n$ if the condition holds for all integers.
	%The map is said to be \emph{null-homotopic} ($\NH$) if it is homotopic to a constant map.
\end{defi}

%There are maps that are $\piT$ but not $\HT$ for singular or \v{C}ech homology. Consider for example the map from a torus to a sphere given by the collapse of its 1-skeleton.

%Naturally, $\HT$ for singular or \v{C}ech homology does not imply $\piT$ either.
%If the map is $\NH$ then it is $\piT$ and, if the value of $\H$ on a point is 0, $\HT$ as well.

%\begin{defi}
%	A space $X$ is said to be $\HLC$ (resp. $\piLC$, $\LC$) if for each $x \in X$ any neighborhood $V$ of $x$ contains a neighborhood $U$ of $x$ such that the inclusion $U \to V$ is $\HT$ (resp. $\piT$, $\NH$).
	%If the neighborhoods can be chosen so that these inclusion have contractible images we say that the space is \textit{locally contractible} ($\LC$).
%\end{defi}

%Local connectivity assumptions like the above ones have a long history of being used to ensure that different homology theories agree, e.g. in \cite{MR105677}, and to ensure that homology is finitely generated, where we mention the following example.
%\begin{prop}[{\citet[p.~109]{MR0007094}}]
%	A compact $\piLC$ Hausdorff space has finite Betti numbers.
%\end{prop}

%We will deduce the following similar result from our main contribution, \cref{t:strong local connectedness implies q-tameness}.

%\begin{prop} \label{prop:HLC_single_space}
%	Let $X$ be a compact Hausdorff space.
%	If $X$ is $\HLC$ then $\H_{n}(X)$ is finitely generated for all $n$.
%\end{prop}

%We mention the following examples of these two uses, recalling that a space is said to be \textit{paracompact} if every open cover has a locally finite open refinement, i.e., every point has a neighborhood intersecting finitely many sets in the refinement.

%\begin{prop}[\citet{MR105677}] \label{prop:cech_sing_hom_hlc}
%	\v{C}ech and singular homology with arbitrary coefficients coincide on the category of paracompact Hausdorff spaces which %are $\HLC$ with respect to integral singular homology.
%\end{prop}

%As a direct consequence of the previous proposition, we obtain the following first persistence result.

%\begin{cor}
%	Let $f \colon X \to \R$ be a function with compact sublevel set filtration. If every sublevel set is $\piLC$ then $\H (X_{\leq \bullet})$ is $\PFD$ in every degree, in particular q-tame.
%\end{cor}
%
%A similar statement with an $\HLC$ condition instead of the $\piLC$ conditions also holds as a consequence of our main theorem. Having each sublevel set being locally connected is, however, in many cases too restrictive. Moreover, the weaker finiteness property of being q-tame is sufficient to obtain a notion of barcode and formulate Morse inequalities.
%Hence, we would like a relative condition for sublevel set filtrations to be sufficient to ensure the q-tameness of the associated persistence module.
% The following definitions are motivated by Morse's work, in particular his local connectivity conditions mentioned in the introduction and reviewed in \cref{s:surfaces}.

\begin{defi} \label{defi:local_connectedness_filtrations}
	The sublevel set filtration of a function $f \colon X \to \R$ is said to be \emph{locally homologically small} or $\HLC$ 
	%(resp.\@ $\piLC$, $\LC$) 
	if for any $x \in X$, any neighborhood $V$ of $x$, and any index $t > f(x)$, there is an index $s$ with  $f(x) < s < t$ and a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion
	\begin{equation*}
	f_{\leq s} \cap U \to f_{\leq t} \cap V
	\end{equation*}
	is $\HS$.
	%(resp.\@ $\piT$, $\NH$).
    %
	Similarly, the sublevel set filtration is called \emph{strongly locally homologically small $\HLC$} or \emph{strongly $\HLC$} if for any $x \in X$, any neighborhood $V$ of $x$, and any pair of indices $s,t$ with $f(x) < s < t$ there is a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion
	\begin{equation*}
	f_{\leq s} \cap U \to f_{\leq t} \cap V
	\end{equation*}
	is $\HS$.
\end{defi}

@@

As our main result, we will now show that for compact sublevel set filtrations the strong $\HLC$ condition implies q-tameness, and consequently also implies the existence of a persistence diagram, yielding persistent Morse inequalities.

@@

\begin{lem} \label{l:key lemma for q-tameness}
    %With the assumptions of \cref{t:strong local connectedness implies q-tameness},
    Let $f \colon X \to \R$ be a function whose sublevel set filtration is compact and strongly $\HLC$, and
    %
	consider subsets $C \subseteq L \subseteq X$ with $C$ compact and $L$ open.
	For any $s < t$ the inclusion
	\[
	C \cap f_{\leq s} \to L \cap f_{\leq t}
	\]
	is $\HS$.
\end{lem}

\begin{proof}
    The statement of the lemma holds for $\HS_{n}$ in place of $\HS$ for any $n \leq n_0$ since $\H_{n}$ induces the zero map.
    We will proceed by induction on $n \geq n_0$ assuming the statement for $\HS_{n-1}$.

    We define $\Sigma_{s, t}$ to be the collection of all open subsets $V \subseteq X$ whose closure $\overline{V}$ is compact, contained in $L$, and has an open neighborhood $U$ with 
	$\overline{V} \subseteq U \subseteq L$
	for which there exists $s' \in (s,\, t)$ such that the inclusion
    $U \cap f_{\leq s'} \to L \cap f_{\leq t}$
	is $\HS_n$.

	We will show that $\Sigma_{s, t}$ has the following three properties:
	\begin{enumerate}
	    \item Any point $x \in L \cap f_{\leq s}$ has a neighborhood $V_x \in \Sigma_{s,t}$.
	    \item If $V_1,\, V_2 \in \Sigma_{s,t}$, then $V_1 \cup V_2 \in \Sigma_{s,t}$.
	    \item For each $V \in \Sigma_{s,t}$ the inclusion 
	    $V \cap f_{\leq s} \to L \cap f_{\leq t}$ 
	    is $\HS_n$.
	\end{enumerate}

	The first property allows us to cover $C$ by sets $V_x \in \Sigma_{s,t}$, $x \in C$. 
	Because $C$ is compact, this cover can be chosen finite, represented by say $x_1,\dots, x_m$. 
	By the second property, we have $V = \bigcup_{i = 1}^m V_{x_i} \in \Sigma_{s,t}$.
	Using the third property, the inclusion 
	$V \cap f_{\leq s} \to L \cap f_{\leq t}$ 
	is $\HS_n$, so the inclusion 
	$C \cap f_{\leq s} \to L \cap f_{\leq t}$ 
	is also $\HS_n$ because this map factors through the aforementioned one.
	What is left to do is to show that $\Sigma_{s,t}$ has the properties we want.

@@

	Finally, we will show using Mayer-Vietoris and the induction hypothesis that $\Sigma_{s,t}$ has the second required property, i.e., that it is closed under finite unions. 
	So for $i \in \{1, 2\}$ let $V_i \in \Sigma_{s,t}$ with $U_i$ and $s'_i \in (s,\, t)$ such that 
	$\overline{V_i} \subseteq U_i \subseteq L$ 
	and
	$U_{i} \cap f_{\leq s'_i} \to L \cap f_{\leq t}$
	is $\HS_n$.
	Writing $K_i = \overline{V_i}$, we use \cref{l:neighborhood third} to construct compact sets $K'_i$ such that
	\[V_i \subseteq K_i \subseteq V'_i \subseteq K'_i \subseteq U_i \subseteq L\]
	where $V'_i = \interior(K'_i)$.
	We have that the union $V_1 \cup V_2 \subseteq L$ is open, its closure $\overline{V_1 \cup V_2}$ is compact, and we have $\overline{V_1 \cup V_2} \subseteq V'_1 \cup V'_2 \subseteq L$. 
	Thus, we obtain $V_1 \cup V_2 \in \Sigma_{s,t}$ if we can show that there is an $s' \in (s,\, t)$ such that the inclusion 
	$\left(V'_1 \cup V'_2 \right) \cap f_{\leq s'} \to L \cap f_{\leq t}$
	is $\HS_n$. 
	To do so, we set $s'' = \min_i s'_i$ and choose $s' \in (s,\, s'')$. 
	For proving that $\left(V'_1 \cup V'_2 \right) \cap f_{\leq s'} \to L \cap f_{\leq t}$ is $\HS_n$ we now distinguish the two cases where $\H$ has either the open or the compact Mayer-Vietoris property.

	In the open case, notice that for both choices of $i$ the inclusions
	$U_i \cap f_{\leq s''} \to L \cap f_{\leq t}$
	are $\HS_n$.
	Additionally, the inclusion
	$V'_1 \cap V'_2 \cap f_{\leq s'} \to U_1 \cap U_2 \cap f_{\leq s''}$
	is $\HS_{n-1}$ because it factors through the inclusion
	$K'_1 \cap K'_2 \cap f_{\leq s'} \to U_1 \cap U_2 \cap f_{\leq s''}$,
	which is $\HS_{n-1}$ by the induction hypothesis.
    Because the $V_i$ and $V'_i$ are open and because $\H$ has the open Mayer-Vietoris property, we obtain the following commutative diagram satisfying the assumptions of \cref{l:commutative algebra}:
	\[
	\begin{tikzcd}[column sep=small]
	\H_n(L \cap f_{\leq t}) \oplus \H_n(L \cap f_{\leq t}) \arrow[r] &
	\H_n(L \cap f_{\leq t}) & \\
	\H_{n}(U_1 \cap f_{\leq s''}) \oplus \H_n(U_2 \cap f_{\leq s''}) \arrow[r] \arrow[u] & 
	\H_{n}((U_1 \cup U_2) \cap f_{\leq s''}) \arrow[r] \arrow[u] &
	\H_{n-1}(U_1 \cap U_2 \cap f_{\leq s''}) \\ & 
	\H_{n}((V'_1 \cup V'_2) \cap f_{\leq s'}) \arrow[r] \arrow[u] &
	\H_{n-1}(V'_1 \cap V'_2 \cap f_{\leq s'}). \arrow[u]
	\end{tikzcd}
	\]
	We conclude that the inclusion 
	$\left(V'_1 \cup V'_2 \right) \cap f_{\leq s'} \to L \cap f_{\leq t}$ 
	is $\HS_n$, which finishes this part of the proof.

	In the compact case, we apply \cref{l:neighborhood third} again to obtain compact sets $K''_i$ such that
	\[V_i \subseteq K_i \subseteq V'_i \subseteq K'_i \subseteq V''_i \subseteq K''_i \subseteq U_i \subseteq L\]
	where $V''_i = \interior(K''_i)$. The rest of the proof is then analogous to the previous case:
	We have that for both choices of $i$ the inclusions
	$K''_i \cap f_{\leq s''} \to L \cap f_{\leq t}$
	are $\HS_n$ because this is true for the corresponding inclusions with $K''_i$ replaced by $U_i$.
	Moreover, the inclusion
	$K'_1 \cap K'_2 \cap f_{\leq s'} \to K''_1 \cap K''_2 \cap f_{\leq s''}$
	is $\HS_{n-1}$ because it factors through the inclusion
	$K'_1 \cap K'_2 \cap f_{\leq s'} \to V''_1 \cap V''_2 \cap f_{\leq s''}$,
	which is $\HS_{n-1}$ by the induction hypothesis.
	Because the $K'_i$ and $K''_i$ as well as the sublevel sets of $f$ are all compact and because $\H$ has the compact Mayer-Vietoris property, we obtain the following commutative diagram satisfying the assumptions of \cref{l:commutative algebra}:
	\[
	\begin{tikzcd}[column sep=small]
	\H_n(L \cap f_{\leq t}) \oplus \H_n(L \cap f_{\leq t}) \arrow[r] &
	\H_n(L \cap f_{\leq t}) & \\
	\H_{n}(K''_1 \cap f_{\leq s''}) \oplus \H_n(K''_2 \cap f_{\leq s''}) \arrow[r] \arrow[u] & 
	\H_{n}((K''_1 \cup K''_2) \cap f_{\leq s''}) \arrow[r] \arrow[u] &
	\H_{n-1}(K''_1 \cap K''_2 \cap f_{\leq s''}) \\ & 
	\H_{n}((K'_1 \cup K'_2) \cap f_{\leq s'}) \arrow[r] \arrow[u] &
	\H_{n-1}(K'_1 \cap K'_2 \cap f_{\leq s'}). \arrow[u]
	\end{tikzcd}
	\]
	We conclude that the inclusion 
	$\left(K'_1 \cup K'_2 \right) \cap f_{\leq s'} \to L \cap f_{\leq t}$
	is $\HS_n$, so the same is true for the inclusion
	$\left(V'_1 \cup V'_2 \right) \cap f_{\leq s'} \to L \cap f_{\leq t}$ 
	because it factors through the previous one. This finishes the proof of the lemma.
\end{proof}

>>>>

Concretely, let $\H = (\H_d)_{d \in \Z} \colon \Top \to \Vect$ be a fixed graded homotopy invariant functor, which we call a \emph{homology theory}.
A triple of spaces $X_{1}, X_{2} \subseteq X$ is said to have a \emph{Mayer-Vietoris sequence} for $\H$ if the inclusion-induced maps fit in a long exact sequence
\begin{equation*}
\begin{tikzcd}[column sep = small]
\cdots \arrow[r] & \H_{n}(X_{1} \cap X_{2}) \arrow[r] & \H_{n}(X_{1}) \oplus \H_{n}(X_{2}) \arrow[r] & \H_{n}(X) \arrow[r] & \H_{n-1}(X_{1} \cap X_{2}) \arrow[r] & \cdots \ .
\end{tikzcd}
\end{equation*}
We say that $\H$ has the \emph{open} (resp.\@\  \emph{compact}) \emph{Mayer-Vietories property} if there are natural Mayer-Vietoris sequences for all triples $X_{1}, X_{2} \subseteq X$ with $X = X_1 \cup X_2$ and $X_i \subseteq X$ open (resp.\@\ compact Hausdorff).

For the rest of this section, we will assume that $\H$ is a homology theory that has either the open or the compact Mayer-Vietoris property and for which there is $n_0$ such that $\H_{n}$ is 0 for all $n \leq n_0$.
Note that this includes singular homology with field coefficients, which, like any homology theory in the sense of the Eilenberg-Steenrod axioms \cite[Section I]{MR0050886}, has the open Mayer-Vietoris property, and it also includes \v{C}ech homology with field coefficients, which has the closed Mayer-Vietoris property.

\begin{defi} \label{defi:local_connectedness}
	For $n \in \Z$ a continuous map is said to be \textit{$n$-homologically small} or $\HS_n$ if the image of the map induced by $\H_{n}$ is finite dimensional.
	%Furthermore, if that image is $0$ then we say that the map is \textit{$n$-homologically trivial} ($\HT_n$).
	%The map is said to be \textit{$n$-homotopically trivial} $(\piT_{n})$ if the map induced by $\pi_{n}$ is 0.
	We omit references to $n$ if the condition holds for all integers.
	%The map is said to be \emph{null-homotopic} ($\NH$) if it is homotopic to a constant map.
\end{defi}

\begin{defi} \label{defi:local_connectedness_filtrations}
	The sublevel set filtration of a function $f \colon X \to \R$ is said to be \emph{locally homologically small} or $\HLC$ if for any $x \in X$, any neighborhood $V$ of $x$, and any index $t > f(x)$, there is an index $s$ with  $f(x) < s < t$ and a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is $\HS$.
\end{defi}
Similarly, we have the following stronger version of this property.
\begin{defi}
	The sublevel set filtration is called \emph{strongly locally homologically small $\HLC$} or \emph{strongly $\HLC$} if for any $x \in X$, any neighborhood $V$ of $x$, and any pair of indices $s,t$ with $f(x) < s < t$ there is a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is $\HS$.
\end{defi}

@@

As our main result, we will now show that for compact sublevel set filtrations the strong $\HLC$ condition implies \mbox{q-tameness}, and consequently also implies the existence of a persistence diagram, yielding persistent Morse inequalities.

@@

\begin{lem} \label{l:key lemma for q-tameness}
    %With the assumptions of \cref{t:strong local connectedness implies q-tameness},
    Let $f \colon X \to \R$ be a function whose sublevel set filtration is compact and strongly $\HLC$, and
    %
	consider subsets $C \subseteq L \subseteq X$ with $C$ compact and $L$ open.
	For any $s < t$ the inclusion
	\begin{equation*}
	C \cap f_{\leq s} \to L \cap f_{\leq t}
	\end{equation*}
	is $\HS$.
\end{lem}

\begin{proof}
	Recall that we are assuming that the underlying homology theory $\H$ has either the open or the compact Mayer-Vietoris property and that there is some $n_0$ such that $\H_{n}$ is 0 for all $n \leq n_0$.
    The statement of the lemma holds for $\HS_{n}$ in place of $\HS$ for any $n \leq n_0$ since $\H_{n}$ induces the zero map.
    We will proceed by induction on $n \geq n_0$ assuming the statement for $\HS_{n-1}$.

    We define $\Sigma_{s, t}$ to be the collection of all open subsets $V \subseteq X$ whose closure $\overline{V}$ is compact, contained in $L$, and has an open neighborhood $U$ with 
	$\overline{V} \subseteq U \subseteq L$
	for which there exists $s' \in (s,\, t)$ such that the inclusion
    $U \cap f_{\leq s'} \to L \cap f_{\leq t}$
	is $\HS_n$.
	We will show that $\Sigma_{s, t}$ has the following three properties:
	\begin{enumerate}
	    \item Any point $x \in L \cap f_{\leq s}$ has a neighborhood $V_x \in \Sigma_{s,t}$.
	    \item If $V_1,\, V_2 \in \Sigma_{s,t}$, then $V_1 \cup V_2 \in \Sigma_{s,t}$.
	    \item For each $V \in \Sigma_{s,t}$ the inclusion 
	    $V \cap f_{\leq s} \to L \cap f_{\leq t}$ 
	    is $\HS_n$.
	\end{enumerate}

	Assuming them for the moment, the first property allows us to cover $C$ by sets $V_x \in \Sigma_{s,t}$, $x \in C$.
	Because $C$ is compact, this cover can be chosen finite, represented by say $x_1,\dots, x_m$.
	By the second property, we have $V = \bigcup_{i = 1}^m V_{x_i} \in \Sigma_{s,t}$.
	Using the third property, the inclusion 
	$V \cap f_{\leq s} \to L \cap f_{\leq t}$ 
	is $\HS_n$, so the inclusion 
	$C \cap f_{\leq s} \to L \cap f_{\leq t}$ 
	is also $\HS_n$ because this map factors through the aforementioned one.
	What is left to do is to show that $\Sigma_{s,t}$ has the properties we want.

@@

	Finally, using Mayer-Vietoris and the induction hypothesis we will show that $\Sigma_{s,t}$ has the second required property, i.e., that it is closed under finite unions.
	So for $i \in \{1, 2\}$ let $V_i \in \Sigma_{s,t}$ with $U_i$ and $s'_i \in (s,\, t)$ such that 
	$\overline{V_i} \subseteq U_i \subseteq L$ 
	and
	$U_{i} \cap f_{\leq s'_i} \to L \cap f_{\leq t}$
	is $\HS_n$.
	Writing $K_i = \overline{V_i}$, we use \cref{l:neighborhood third} to construct compact sets $K'_i$ such that
	\begin{equation*}
	V_i \subseteq K_i \subseteq V'_i \subseteq K'_i \subseteq U_i \subseteq L
	\end{equation*}
	where $V'_i = \interior(K'_i)$.
	We have that the union $V_1 \cup V_2 \subseteq L$ is open, its closure $\overline{V_1 \cup V_2}$ is compact, and we have $\overline{V_1 \cup V_2} \subseteq V'_1 \cup V'_2 \subseteq L$.
	Thus, we obtain $V_1 \cup V_2 \in \Sigma_{s,t}$ if we can show that there is an $s' \in (s,\, t)$ such that the inclusion 
	$\left(V'_1 \cup V'_2 \right) \cap f_{\leq s'} \to L \cap f_{\leq t}$
	is $\HS_n$.
	To do so, we set $s'' = \min_i s'_i$ and choose $s' \in (s,\, s'')$.
	For proving that $\left(V'_1 \cup V'_2 \right) \cap f_{\leq s'} \to L \cap f_{\leq t}$ is $\HS_n$ we now distinguish the two cases where $\H$ has either the open or the compact Mayer-Vietoris property.

	In the open case, notice that for both choices of $i$ the inclusions
	$U_i \cap f_{\leq s''} \to L \cap f_{\leq t}$
	are $\HS_n$.
	Additionally, the inclusion
	$V'_1 \cap V'_2 \cap f_{\leq s'} \to U_1 \cap U_2 \cap f_{\leq s''}$
	is $\HS_{n-1}$ because it factors through the inclusion
	$K'_1 \cap K'_2 \cap f_{\leq s'} \to U_1 \cap U_2 \cap f_{\leq s''}$,
	which is $\HS_{n-1}$ by the induction hypothesis.
    Because the $V_i$ and $V'_i$ are open and because $\H$ has the open Mayer-Vietoris property, we obtain the following commutative diagram satisfying the assumptions of \cref{l:commutative algebra}:
	\begin{equation*}
	\begin{tikzcd}[column sep=small]
	\H_n(L \cap f_{\leq t}) \oplus \H_n(L \cap f_{\leq t}) \arrow[r] &
	\H_n(L \cap f_{\leq t}) & \\
	\H_{n}(U_1 \cap f_{\leq s''}) \oplus \H_n(U_2 \cap f_{\leq s''}) \arrow[r] \arrow[u] & 
	\H_{n}((U_1 \cup U_2) \cap f_{\leq s''}) \arrow[r] \arrow[u] &
	\H_{n-1}(U_1 \cap U_2 \cap f_{\leq s''}) \\ & 
	\H_{n}((V'_1 \cup V'_2) \cap f_{\leq s'}) \arrow[r] \arrow[u] &
	\H_{n-1}(V'_1 \cap V'_2 \cap f_{\leq s'}). \arrow[u]
	\end{tikzcd}
	\end{equation*}
	We conclude that the inclusion 
	$\left(V'_1 \cup V'_2 \right) \cap f_{\leq s'} \to L \cap f_{\leq t}$ 
	is $\HS_n$, which finishes this part of the proof.

	In the compact case, we apply \cref{l:neighborhood third} again to obtain compact sets $K''_i$ such that
	\begin{equation*}
	V_i \subseteq K_i \subseteq V'_i \subseteq K'_i \subseteq V''_i \subseteq K''_i \subseteq U_i \subseteq L
	\end{equation*}
	where $V''_i = \interior(K''_i)$.
	The rest of the proof is then analogous to the previous case:
	We have that for both choices of $i$ the inclusions
	$K''_i \cap f_{\leq s''} \to L \cap f_{\leq t}$
	are $\HS_n$ because this is true for the corresponding inclusions with $K''_i$ replaced by $U_i$.
	Moreover, the inclusion
	$K'_1 \cap K'_2 \cap f_{\leq s'} \to K''_1 \cap K''_2 \cap f_{\leq s''}$
	is $\HS_{n-1}$ because it factors through the inclusion
	$K'_1 \cap K'_2 \cap f_{\leq s'} \to V''_1 \cap V''_2 \cap f_{\leq s''}$,
	which is $\HS_{n-1}$ by the induction hypothesis.
	Because the $K'_i$ and $K''_i$ as well as the sublevel sets of $f$ are all compact and because $\H$ has the compact Mayer-Vietoris property, we obtain the following commutative diagram satisfying the assumptions of \cref{l:commutative algebra}:
	\begin{equation*}
	\begin{tikzcd}[column sep=small]
	\H_n(L \cap f_{\leq t}) \oplus \H_n(L \cap f_{\leq t}) \arrow[r] &
	\H_n(L \cap f_{\leq t}) & \\
	\H_{n}(K''_1 \cap f_{\leq s''}) \oplus \H_n(K''_2 \cap f_{\leq s''}) \arrow[r] \arrow[u] & 
	\H_{n}((K''_1 \cup K''_2) \cap f_{\leq s''}) \arrow[r] \arrow[u] &
	\H_{n-1}(K''_1 \cap K''_2 \cap f_{\leq s''}) \\ & 
	\H_{n}((K'_1 \cup K'_2) \cap f_{\leq s'}) \arrow[r] \arrow[u] &
	\H_{n-1}(K'_1 \cap K'_2 \cap f_{\leq s'}). \arrow[u]
	\end{tikzcd}
	\end{equation*}
	We conclude that the inclusion 
	$\left(K'_1 \cup K'_2 \right) \cap f_{\leq s'} \to L \cap f_{\leq t}$
	is $\HS_n$, so the same is true for the inclusion
	$\left(V'_1 \cup V'_2 \right) \cap f_{\leq s'} \to L \cap f_{\leq t}$ 
	because it factors through the previous one.
\end{proof}

### 2021-07-16 introduction.tex
Improve sect 4

The interplay between the critical set of a function and the topology of its domain is a cornerstone of modern mathematics.
Nowadays, when thinking about the pioneering work of Marston Morse, our first thought probably considers a differentiable function on a closed smooth manifold, but more general settings should also come to mind.
Morse theory in the smooth context was masterfully presented in Milnor's famous book on the subject \cite{MR0163331}, where he also gave a new proof of Bott's periodicity by applying Morse theory to the energy functional of paths in a Riemannian manifold.
Another important example of the use of Morse's insights in an infinite context is Floer's work on the Arnold conjecture and its many ramifications in symplectic topology, as surveyed for example in \cite{MR1702944}.
Morse himself worked in a very general setting, publishing in the 1930s a series of papers \cite{Morse.1937, Morse.1938, Morse.1940, MR9102} in which he established the key results of Morse theory in the broad context defined by semi-continuous functionals on metric spaces.
He named this body of work \emph{functional topology} and used it to study minimal surfaces motivated by Douglas' solution to Plateau’s Problem \cite{Douglas.1931}.
In particular, Morse and Tompkins \cite{Morse.1939, Morse.1941} used these techniques to prove the Unstable Minimal Surface Theorem, a result providing conditions for the existence of critical points of the Douglas functional that are not local minima.

>>>>

The interplay between the critical set of a function and the topology of its domain is a cornerstone of modern mathematics.
Nowadays, when thinking about the pioneering work of Marston Morse, our first thought probably considers a differentiable function on a closed smooth manifold, but more general settings should also be regarded.
Morse theory in the smooth context was masterfully presented in Milnor's famous book on the subject \cite{MR0163331}, where he also gave a new proof of Bott's periodicity by applying Morse theory to the energy functional of paths in a Riemannian manifold.
Another important example of the use of Morse's insights in an infinite context is Floer's work on the Arnold conjecture and its many ramifications in symplectic topology, as surveyed for example in \cite{MR1702944}.
Morse himself worked in a very general setting, publishing in the 1930s a series of papers \cite{Morse.1937, Morse.1938, Morse.1940, MR9102} in which he established the key results of Morse theory in the broad context defined by semi-continuous functionals on metric spaces.
He named this body of work \emph{functional topology} and used it to study minimal surfaces motivated by Douglas' solution to Plateau’s Problem \cite{Douglas.1931}.
In particular, Morse and Tompkins \cite{Morse.1939, Morse.1941} used these techniques to prove the Unstable Minimal Surface Theorem, a result providing conditions for the existence of critical points of the Douglas functional that are not local minima.

### 2021-07-16 main.tex
Improve sect 3
Improve sect 4

% commands
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\HS}{\mathrm{HS}}
\newcommand{\HT}{\mathrm{HT}}
\newcommand{\HLC}{\mathrm{LHS}}
\newcommand{\piT}{\pi\mathrm{T}}
\newcommand{\LC}{\mathrm{LC}}
\newcommand{\NH}{\mathrm{NH}}
\newcommand{\piLC}{\pi\mathrm{LC}}
\newcommand{\HE}{\mathbb{H}^d}
\renewcommand{\H}{H}
\DeclareMathOperator{\interior}{int}
\DeclareMathOperator{\im}{im}
\DeclareMathOperator{\coker}{coker}
\DeclareMathOperator{\rad}{rad}
\newcommand\CH{\check{H}}
\newcommand{\Mod}[1]{#1-\mathbf{Mod}}
\newcommand{\PFD}{\mathrm{PFD}}
\newcommand{\PFG}{\mathrm{PFG}}
\DeclareMathOperator{\Nrv}{Nrv}
\DeclareMathOperator{\Cov}{Cov}
\DeclareMathOperator{\Vietoris}{Vtr}
\DeclareMathOperator{\Balls}{Balls}
\DeclareMathOperator*{\colim}{colim}
\DeclareMathOperator{\crit}{crit}
\newcommand\MCH{M\check{H}}
\newcommand\VH{VH}
\newcommand\MVH{MVH}
\newcommand{\obs}{\dashrightarrow}
\newcommand{\multiplicityDomain}{\mathcal{E}}
\newcommand{\Top}{\mathsf{Top}}
\newcommand{\Vect}{\mathsf{Vect}}
\newcommand{\anibal}[1]{\textcolor{blue}{\underline{Anibal}: #1}}

@@

\institute{
    Ulrich Bauer \at Technical University of Munich \\ \email{mail@ulrich-bauer.org} \and
	Anibal M.~Medina-Mardones \at Max Planck Institute for Mathematics, Bonn \\ \email{ammedmar@mpim-bonn.mpg.de} 
	\and
	Maximilian Schmahl \at Heidelberg University \\ \email{mschmahl@mathi.uni-heidelberg}
}

\authorrunning{U.~Bauer, A.~M.~Medina-Mardones, M.~Schmahl}

>>>>

% commands
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\HS}{\mathrm{HS}}
\newcommand{\HT}{\mathrm{HT}}
\newcommand{\HLC}{\mathrm{LHS}}
\newcommand{\piT}{\pi\mathrm{T}}
\newcommand{\LC}{\mathrm{LC}}
\newcommand{\NH}{\mathrm{NH}}
\newcommand{\piLC}{\pi\mathrm{LC}}
\newcommand{\HE}{\mathbb{H}^d}
\renewcommand{\H}{H}
\DeclareMathOperator{\interior}{int}
\DeclareMathOperator{\im}{im}
\DeclareMathOperator{\coker}{coker}
\DeclareMathOperator{\rad}{rad}
\newcommand\CH{\check{H}}
\newcommand{\Mod}[1]{#1-\mathbf{Mod}}
\newcommand{\PFD}{\mathrm{PFD}}
\newcommand{\PFG}{\mathrm{PFG}}
\DeclareMathOperator{\Nrv}{Nrv}
\DeclareMathOperator{\Cov}{Cov}
\DeclareMathOperator{\Vietoris}{Vtr}
\DeclareMathOperator{\Balls}{Balls}
\DeclareMathOperator*{\colim}{colim}
\DeclareMathOperator{\crit}{crit}
\newcommand\MCH{M\check{H}}
\newcommand\VH{VH}
\newcommand\MVH{MVH}
\newcommand{\obs}{\dashrightarrow}
\newcommand{\multiplicityDomain}{\mathcal{E}}
\newcommand{\Top}{\mathsf{Top}}
\newcommand{\Vect}{\mathsf{Vect}}
\renewcommand{\th}{^{\mathrm{th}}}
\newcommand{\anibal}[1]{\textcolor{blue}{\underline{Anibal}: #1}}

@@

\institute{
    Ulrich Bauer \at Technical University of Munich \\ \email{mail@ulrich-bauer.org} \and
	Anibal M.~Medina-Mardones \at Max Planck Institute for Mathematics in Bonn \at Department of Mathematics, University of Notre Dame \\ \email{ammedmar@mpim-bonn.mpg.de} 
	\and
	Maximilian Schmahl \at Heidelberg University \\ \email{mschmahl@mathi.uni-heidelberg}
}

\authorrunning{U.~Bauer, A.~Medina-Mardones, M.~Schmahl}
